\chapter{Ring Theory}
\textbf{R1:} Let $R=\mathbb{Z}[\sqrt{-3}]=\{a+b \sqrt{-3}: a, b \in \mathbb{Z}\}$.\\
(a) Why is $R$ an integral domain?\\
(b) What are the units in $R$ ?\\
(c) Is the element 2 irreducible in $R$ ?\\
(d) If $x, y \in R$, and 2 divides $x y$, does it follow that 2 divides either $x$ or $y$ ? Justify your answer.

R2. (a) Give an example of an integral domain with exactly 9 elements.\\
(b) Is there an integral domain with exactly 10 elements? Justify your answer.

R3. Let

$$
F=\left\{\left[\begin{array}{cc}
	a & b \\
	2 b & a
\end{array}\right]: a, b \in \mathbb{Q}\right\} .
$$

(a) Prove that $F$ is a field under the usual matrix operations of addition and multiplication.\\
(b) Prove that $F$ is isomorphic to the field $\mathbb{Q}(\sqrt{2})$.

R3. Let $\mathbb{F}$ be a field and let $R=\mathbb{F}[X, Y]$ be the ring of polynomials in $X$ and $Y$ with coefficients from $\mathbb{F}$.\\
(a) Show that $M=\langle X+1, Y-2\rangle$ is a maximal ideal of $R$.\\
(b) Show that $P=\langle X+Y+1\rangle$ is a prime ideal of $R$.\\
(c) Is $P$ a maximal ideal of $R$ ? Justify your answer.

R4. Let $R$ be an integral domain containing a field $k$ as a subring. Suppose that $R$ is a finite-dimensional vector space over $k$, with scalar multiplication being the multiplication in $R$. Prove that $R$ is a field.\\
R5. Let $R$ be a commutative ring with identity and let $I$ and $J$ be ideals of $R$.\\
(a) Define

$$
(I: J)=\{r \in R: r x \in I \text { for all } x \in J\}
$$

Show that $(I: J)$ is an ideal of $R$ containing $I$.\\
(b) Show that if $P$ is a prime ideal of $R$ and $x \notin P$, then $(P:\langle x\rangle)=P$, where $\langle x\rangle$ denotes the principal ideal generated by $x$.\\
(a) Define what is meant by the sum $I+J$ and the product $I J$ of the ideals $I$ and $J$.\\
(b) If $I$ and $J$ are distinct maximal ideals, show that $I+J=R$ and $I \cap J=I J$.

R6. Let $\mathbb{F}_{2}$ be the field with 2 elements.\\
(a) Show that $f(X)=X^{3}+X^{2}+1$ and $g(X)=X^{3}+X+1$ are the only irreducible polynomials of degree 3 in $\mathbb{F}_{2}[X]$.\\
(b) Give an explicit field isomorphism

$$
\mathbb{F}_{2}[X] /\langle f(X)\rangle \cong \mathbb{F}_{2}[X] /\langle g(X)\rangle
$$

R7. Show that $\mathbb{Z}[i] /\langle 1+i\rangle$ is isomorphic to the field $\mathbb{F}_{2}$ with 2 elements. As usual, $i$ denotes the complex number $\sqrt{-1}$ and $\langle 1+i\rangle$ denotes the principal ideal of $\mathbb{Z}[i]$ generated by $1+i$.\\
R8. Consider the ring $\mathbb{Z}[X]$ of polynomials in one variable $X$ with coefficients in $\mathbb{Z}$.\\
(a) Find all the units of $\mathbb{Z}[X]$.\\
(b) Describe an easy way to recognize the elements of the ideal $I$ of $\mathbb{Z}[X]$ generated by 2 and $X$.\\
(c) Find a prime ideal of $\mathbb{Z}[X]$ that is not maximal.

R9. Determine, with justification, all of the irreducible polynomials of degree 4 over the field $\mathbb{F}_{2}$ of two elements.\\
R10. Let $R=\mathbb{Z}[\sqrt{-10}]$.\\
(a) Show that $R$ is not a PID. (Hint: Show that 10 admits two essentially different factorizations into irreducible elements of $R$.)\\
(b) Let $P=\langle 7,5+\sqrt{-10}\rangle$. Show that $R / P$ is isomorphic to $\mathbb{Z} / 7 \mathbb{Z}$.

R11. Suppose that $R$ is an integral domain and $X$ is an indeterminate.\\
(a) Prove that if $R$ is a field, then the polynomial ring $R[X]$ is a PID (principal ideal domain).\\
(b) Show, conversely, that if $R[X]$ is a PID, then $R$ is a field.

R12. (a) Prove that every Euclidean domain is a principal ideal domain (PID).\\
(b) Give an example of a unique factorization domain that is not a PID and justify your answer.

R13. (a) Show that for each natural number $n \in \mathbb{N}$, there is an irreducible polynomial $P_{n}(X) \in \mathbb{Q}[X]$ of degree $n$.\\
(b) Is this true when $\mathbb{Q}$ is replaced by $\mathbb{R}$ ? Explain.

R14. Let $R$ be a commutative ring with identity. If $I \subseteq R$ is an ideal, then the radical of $I$, denoted $\sqrt{I}$, is defined by

$$
\sqrt{I}=\left\{a \in R: a^{n} \in I \text { for some positive integer } n\right\}
$$

(a) Prove that $\sqrt{I \cap J}=\sqrt{I} \cap \sqrt{J}$.\\
(b) If $P$ is a prime ideal of $R$ and $r \in \mathbb{N}$, find $\sqrt{P^{r}}$ and justify your answer.\\
(c) Find $\sqrt{I}$, where $I$ is the ideal $\langle 108\rangle$ in the ring $\mathbb{Z}$ of integers.

R15. (a) Show that $\mathbb{Z}[i] /\langle 3+i\rangle \cong \mathbb{Z} / 10 \mathbb{Z}$, where $i$ is the usual complex number $\sqrt{-1}$.\\
(b) Is $\langle 3+i\rangle$ a maximal ideal of $\mathbb{Z}[i]$ ? Give a reason for your answer.

R16. Let $R=\mathbb{Z}[X]$. Answer the following questions about the ring $R$. You may quote an appropriate theorem, provide a counterexample, or give a short proof to justify your answer.\\
(a) Is $R$ a unique factorization domain?\\
(b) Is $R$ a principal ideal domain?\\
(c) Find the group of units of $R$.\\
(d) Find a prime ideal of $R$ which is not maximal.\\
(e) Find a maximal ideal of $R$.

R17. An element $a$ in a ring $R$ is nilpotent if $a^{n}=0$ for some natural number $n$.\\
(a) If $R$ is a commutative ring with identity, show that the set of nilpotent elements forms an ideal.\\
(b) Describe all of the nilpotent elements in the ring $\mathbb{C}[X] /\langle f(X)\rangle$, where

$$
f(X)=(X-1)\left(X^{2}-1\right)\left(X^{3}-1\right)
$$

(c) Show that part (a) need not be true if $R$ is not commutative. (Hint: Try a matrix ring.)

R18. Let $R$ be a ring, let $R^{*}$ be the set of units of $R$, and let $M=R \backslash R^{*}$. If $M$ is an ideal, prove that $M$ is a maximal ideal and that moreover it is the only maximal ideal of $R$.\\
R19. (a) Let $R$ be a PID and let $I, J$ be nonzero ideals of $R$. Show that $I J=I \cap J$ if and only if $I+J=R$.\\
(b) Show that $\mathbb{Z} / 900 \mathbb{Z}$ is isomorphic to $\mathbb{Z} / 100 \mathbb{Z} \oplus \mathbb{Z} / 9 \mathbb{Z}$ as rings.\\
(a) Let $I=\left\langle X^{2}+2,5\right\rangle \subseteq \mathbb{Z}[X]$ and let $J=\left\langle X^{2}+2,3\right\rangle$. Show that $I$ is a maximal ideal, but $J$ is not a maximal ideal.\\
R20. Let $F$ be a subfield of a field $K$ and let $f(X), g(X) \in F[X] \backslash\{0\}$. Prove that the greatest common divisor of $f(X)$ and $g(X)$ in $F[X]$ is the same as the greatest common divisor taken in $K[X]$.\\
R21. Find the greatest common divisor of $X^{3}-6 X^{2}+X+4$ and $X^{5}-6 X+1$ in $\mathbb{Q}[X]$.\\
R22. Define $\varphi: \mathbb{C}[X, Y] \rightarrow \mathbb{C}[T]$ by $\varphi(X)=T^{2}, \varphi(Y)=T^{3}$.\\
(a) Show that $\operatorname{Ker}(\varphi)=\left\langle Y^{2}-X^{3}\right\rangle$.\\
(b) Find the image of $\varphi$.

R23. Prove that $\mathbb{Z}[\sqrt{-2}]$ is a Euclidean domain.\\
R24. Let $m, n$ be two non-zero integers. Prove that the greatest common divisor of $m$ and $n$ in $\mathbb{Z}$ is the same as the greatest common divisor taken in $\mathbb{Z}[i]$. Generalize this to a statement about the greatest common divisor of elements $a$ and $b$ in a Euclidean domain $R$ which is a subring of a Euclidean domain $S$.

R25. Prove that the center of the matrix ring $M_{n}(\mathbb{R})$ is the set of scalar matrices, i.e., $C\left(M_{n}(\mathbb{R})\right)=\left\{a I_{n}\right.$ : $a \in \mathbb{R}\}$.

R26. Let $R_{1}=\mathbb{F}_{p}[X] /\left\langle X^{2}-2\right\rangle$ and $R_{2}=\mathbb{F}_{p}[X] /\left\langle X^{2}-3\right\rangle$ where $\mathbb{F}_{p}$ is the field of $p$ elements, $p$ a prime. Determine if $R_{1}$ is isomorphic to $R_{2}$ in each of the cases $p=2, p=5$, and $p=11$.\\
R27. (a) Show that the only automorphism of the field $\mathbb{R}$ of real numbers is the identity.\\
(b) Show that any automorphism of the field $\mathbb{C}$ of complex numbers which fixes $\mathbb{R}$ is either the identity or complex conjugation.\\
R28. (a) Find all ideals of the ring $\mathbb{Z} / 24 \mathbb{Z}$.\\
(b) Find all ideals of the ring $\mathbb{Q}[X] /\left\langle X^{2}+2 X-2\right\rangle$.

R29. Let $R$ be an integral domain. Show that the group of units of the polynomial ring $R[X]$ is equal to the group of units of the ground ring $R$.\\
R30. Express the polynomial $X^{4}-2 X^{2}-3$ as a product of irreducible polynomials over each of the following fields: $\mathbb{Q}, \mathbb{R}, \mathbb{C}, \mathbb{F}_{5}$.\\
R31. Let $\omega=(1+\sqrt{-3}) / 2 \in \mathbb{C}$ and let $R=\{a+b \omega: a, b \in \mathbb{Z}\}$.\\
(a) Show that $R$ is a subring of $\mathbb{C}$.\\
(b) Show that $R$ is a Euclidean domain with respect to the norm function $N(z)=z \bar{z}$, where, as usual, $\bar{z}$ denotes the complex conjugate of $z$.\\
R32. Let $I$ be an ideal of $\mathbb{R}[X]$ generated by an irreducible polynomial of degree 2 . Show that $\mathbb{R}[X] / I$ is isomorphic to the field $\mathbb{C}$.\\
R33. Show that in the ring $M$ of $2 \times 2$ real matrices (with the usual sum and multiplication of matrices), the only 2 -sided ideals are $\langle 0\rangle$ and the whole ring $M$.\\
R34. Let $R$ be a commutative ring with identity. Suppose $a \in R$ is a unit and $b \in R$ is nilpotent. Show that $a+b$ is a unit.\\
R35. (b) Let $R$ and $S$ be commutative rings with identities $1_{R}$ and $1_{S}$, respectively, let $f: R \rightarrow S$ be a ring homomorphism such that $f\left(1_{R}\right)=1_{S}$. If $P$ is a prime ideal of $S$ show that $f^{-1}(P)$ is a prime ideal of $R$.\\
(c) Let $f$ be as in part (b). If $M$ is a maximal ideal of $S$, is $f^{-1}(M)$ a maximal ideal of $R$ ? Prove that it is or give a counterexample.\\
R36. (a) Let $\mathbb{H}$ be the ring of quaternions, $q=a+b \mathbf{i}+c \mathbf{j}+d \mathbf{k}$, where $\mathbf{i}^{2}=\mathbf{j}^{2}=\mathbf{k}^{2}=\mathbf{i j k}=-1,, a, b, c, d \in \mathbb{R}$. Let $q^{*}=a-b \mathbf{i}-c \mathbf{j}-d \mathbf{k}$ and $\|q\|^{2}=q q^{*}=a^{2}+b^{2}+c^{2}+d^{2}$. Show that the set $\mathbb{H}_{1}$ of quaternions with $\|q\|=1$ is a group under quaternion multiplication. Hint: show $\left(q_{1} q_{2}\right)^{*}=q_{2}^{*} q_{1}^{*}$ and use $q^{* *}=q, a^{*}=a$ for $a \in \mathbb{R}$.\\
(b) Show that the map

$$
\mathbb{H} \rightarrow M_{2}(\mathbb{C}), \quad q=a+b \mathbf{i}+c \mathbf{j}+d \mathbf{k} \mapsto M(q):=\left[\begin{array}{cc}
	a+b i & c+d i \\
	-c+d i & a-b i
\end{array}\right] \quad i=\sqrt{-1},
$$

is an $\mathbb{R}$-algebra homomorphism, and that $\|q\|^{2}=\operatorname{det} M(q)$.\\
R37. Let $\mathbb{H} \rightarrow M_{2}(\mathbb{C})$ be the ring homomorphism of part (b) of problem R40. Show that this induces an isomorphism

$$
\mathbb{H}_{1} \cong S U_{2}=\left\{T \in M_{2}(\mathbb{C}) \mid T^{t} \bar{T}=I_{2}, \operatorname{det} T=1\right\}
$$

R38. Let $\mathbb{H}_{1} \rightarrow S U_{2}$ be the isomorphism of R 41 . For each $q \in \mathbb{H}_{1}$, define a map $\mathbb{R}^{3} \rightarrow \mathbb{R}^{3}$ :

$$
\mathbf{v}=\left(\begin{array}{l}
	a \\
	b \\
	c
\end{array}\right) \mapsto R_{q}(\mathbf{v})=\left(\begin{array}{l}
	a^{\prime} \\
	b^{\prime} \\
	c^{\prime}
\end{array}\right)
$$

by the rule $q(a \mathbf{i}+b \mathbf{j}+c \mathbf{k}) q^{*}=a^{\prime} \mathbf{i}+b^{\prime} \mathbf{j}+c^{\prime} \mathbf{k}$. Show that this makes sense: the quaternion $q(a \mathbf{i}+b \mathbf{j}+c \mathbf{k}) q^{*}$ has only $\mathbf{i}, \mathbf{j}, \mathbf{k}$ components. The $\operatorname{map} \mathbf{v} \mapsto R_{q}(\mathbf{v})$ is clearly an invertible $\mathbb{R}$-linear map, hence an element of $G L(3, \mathbb{R})$. Now show that it preserves the dot-product of vectors in $\mathbb{R}^{3},\left(a_{1}, b_{1}, c_{1}\right) \cdot\left(a_{2}, b_{2}, c_{2}\right)=$ $a_{1} a_{2}+b_{1} b_{2}+c_{1} c_{2}$, that is

$$
R_{q}\left(\mathbf{v}_{1}\right) \cdot R_{q}\left(\mathbf{v}_{2}\right)=\mathbf{v}_{1} \cdot \mathbf{v}_{2} .
$$

Hint: Let quat $(a, b, c)=a \mathbf{i}+b \mathbf{j}+c \mathbf{k}$, then

$$
\mathbf{v}_{1} \cdot \mathbf{v}_{2}=\left[\operatorname{quat}\left(\mathbf{v}_{1}\right) \operatorname{quat}\left(\mathbf{v}_{2}\right)^{*}+\operatorname{quat}\left(\mathbf{v}_{2}\right) \operatorname{quat}\left(\mathbf{v}_{1}\right)^{*}\right] / 2 .
$$

Therefore $R_{q} \in S O_{3}(\mathbb{R})=\left\{T \in M_{3}(\mathbb{R}) \mid T^{t} T=I_{3}, \operatorname{det} T=1\right\}$.\\
R39. Show that the map $q \mapsto R_{q}$ is a homomorphism $\mathbb{H}_{1} \rightarrow S O(3, \mathbb{R})$, i.e., $R_{q_{1} q_{2}}=R_{q_{1}} R_{q_{2}}$. Show that it induces an isomorphism $S U_{2} / \pm 1 \cong S O(3, \mathbb{R})$.